---
title: "Student Sit In"
author: "Servio Maldonado"
date: "10/26/2019"
output: 
  html_document:
    toc: true
    number_sectons: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ONE SHOT assignment!
this is an extra credit assignment, must be completed Monday Oct 28, turn-in closes at midnight!

## Problem statement: 
Students at UCD- is there a relation between where one sits and one's major? 

## Introduction  

<!-- where is the data found?  Is this an experiment or an observational study?  !-->

Data from this study came from the UCDataframe with multiple variables out of 173 students.



```{r include=FALSE, echo=FALSE}
library(tigerstats)
data(ucdavis1)

```

$H_0$: there is no relationship between one's major and where one sits in a class   
$H_A$: where one sits in class and one's major are related  

<!-- Get the data: !-->


```{r echo=FALSE}
UCDdataframe = data.frame(seat=ucdavis1$Seat, major=ucdavis1$class, data=ucdavis1)
names(UCDdataframe)
```
## Methods

<!--  describe analysis methods here 
what are the variable types, and indicate gaphical, numerical, and inferential methods appropriate
for this question  !--> 

The Methods that we will be using for this experiment are graphical barcharts, numerical tables and inferential methods to find the p-value to find out if there is any correlation between where one sits and ones major.

## Data summary

**Graphical summary**


```{r}
barchartGC(~seat+major, data=UCDdataframe, main='seating+major ', type='percent', xlab='seat')

```


The graph shows that Non-Liberal Arts majors prefer the back and middle seats a little more than the front but not by much and Liberal Arts majors prefer the front more than the middle and back. But neither likes one seat predominantly more than the other.


**Numerical summary**


```{r}
xtab=xtabs(~seat+major,data=UCDdataframe)
print(xtab)
```

There is not much of a difference between seating preference between majors.


## Inferential Results


```{r}

chisqtestGC(xtab)
```

The P-Value is 0.2173 > 0.05 suggest there is no connection between where one sits and ones major.

## Results and conclusions

<!-- explain-- is there evidence that certain majors tend to sit in particular areas of the class?  Can the results of this test be generalized to all majors in all universities? !-->

There is no evidence that certain majors lend to sit in particular areas of the class. The P-value was 0.2173 which is greater than 0.05 so we fail to reject the hypothesis.


<!--
push results to your github account, turn in the URL

--OR--

If you did not fork my repo to your github account,
create a repository in your github account for this project, get the URL for that repo and 
(in the terminal window..)

$git remote add origin URL_of_your_github_repo
$git push -u origin master

!-->